F-stats vs PCA

### 2021-04-20 fstats_pca.tex
intro

>>>>

	\subsection{$F_2$ error}
	In most $F$-statistics applications, $F_2$ is \emph{estimated} using the minimum-variance unbiased estimator \citep{reich2009}
	\begin{subequations}

	\begin{equation}
	f_2(X_1, X_2) = \frac{1}{L}\sum_l (x_{l1} - x_{l2})^2 - \frac{1}{L}\sum_l\frac{x_{l1} (1-x_{l1})}{n_{l1}-1} - 
	\frac{1}{L}\sum_l\frac{x_{l2} (1-x_{l2})}{n_{l2}-1} - 
	\end{equation}
	in contrast, as shown above, PCA can be thought as a decomposition of a matrix of uncorrected $F_2$-statistics:
	\begin{equation}
	F_2(X_1, X_2) = \frac{1}{L}\sum_l(x_{l1} - x_{l2})^2
	\end{equation}
	\end{subequations}

	This leads to some issues, for example trying to perform a PCA on the matrix of $f_2$-values is not positive semidefinite, and so some principal components may be imaginary. One possible resolution is probabilistic PCA \citep[e.g.][]{engelhardt2010,agrawal2020}.

	\begin{align}
	    y_{ij} | \MP_{ij}, \epsilon_i &= (\MP\ML)_{ij} + \epsilon_{ij}\nonumber\\
	    x_i & \sim N(0, \mathbf{I}) \nonumber\\
	    \epsilon_i &\sim N(0, \sigma^2 \mathbf{I})\nonumber
	\end{align}
